Kung Faux Pandas \\ \large Alternative Facts for Privacy Preservation

### 2018-05-07 paper/main.tex
Auto Update from local Sharelatex

\usepackage{url}

@@

%\author{James King \& Seth Russel}
\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V) \\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  \texttt{james.king@ucdenver.edu} \\ 
  \texttt{seth.russell@ucdenver.edu} \\
  }

@@

% Tell:  articulate the problem with evidence (i.e. papers)
%   Enable reproducibility - patient value, make process of replication easier
%   Time saving
%   legal risk (carrying data in laptops, etc)
%   Multiple comparison?
%   Educational data sets

@@

>>>>

@@

%\author{James King \& Seth Russel}
\author{
  James King \& Seth Russell\\
  Data Science to Patient Value (D2V)\\
  School of Medicine \\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{james.king@ucdenver.edu} \\ 
  \texttt{seth.russell@ucdenver.edu} \\
  }

@@

% Advice from Tell:  articulate the problem with evidence (i.e. papers)
%   Enable reproducibility - patient value, make process of replication easier
%   Time saving
%   legal risk (carrying data in laptops, etc)
%   Multiple comparison?
%   Educational data sets

@@

Reproducing Machine learning requires access to source data
Source data is hard to get
In medical field, harder to get than most fields – IRBs, HIPAA regulation, etc.
Various methods used to synthesize or de-identify

A wide array of methods and techniques have been developed for generating synthetic data sas  data \cite{walonoski_synthea:_2018}
